Multi-level modeling with Openflexo/\FML

### 2021-09-22 9-relatedworks.tex
adding comments to the related work section...

>>>>

\noteSM{so... to please reviewer 2 we should improve this section, notably better compare approaches. I am thinking about a table...}

\noteSM{Our solution relies on the use of the type/object pattern for achieving ontological instantiation and the core capacity of Openflexo/FML to reference models disregarding abstraction levels. Our solution uses a metamodel to group the required concepts for describing universal processes and an extending metamodel that adapts it to the domain of software engineering processes. Process instances reference elements from both metamodels.}

\noteSM{Add some infor about how constraints are managed in each of the approaches.}
